Off the beaten path: \\ Gaia reveals GD-1 stars perturbed off of the main stream track

### 2018-04-30 paper/gd1.tex
orbit figure
discussion points

- smooth component of the potential?
-- show orbit
-- chaos?
-- bar?

@@

- future:
-- radial velocities, measure 3d velocity structure (unique predictions)
-- tests for other outstanding issues
-- model facets of stream morphology to ascertain if consistent with encounter signatures
-- so far a lot of focus on gaps produced in encounters -- extra features we detected beside the GD-1 track suggest that further theoretical focus on scattered material is needed to fully understand its dynamical history

>>>>

- spur & blob as related to gaps? -- classify possible explanations in this way
- if from encounter -- could get more info on the perturber than from the gaps alone, say from delta v

- progenitor
-- rotation -- could explain spurs, but not gaps?

- smooth component of the potential?
-- show orbit
-- chaos?
-- \todo{APW} bar -- hard to make small feature, size should be ~angular size of the bar at stream (influence of bar should be a radian of the stream) + relative velocity (retrograde)

@@

- future:
-- radial velocities, measure 3d velocity structure (unique predictions)
- delta energy, 
- cleaner selection (any stars in the gap)

- (should go at least to symmetric in positive), not captured with naive selection, as there are gradients
- prediction: very negative rv, should be easy to map the full extent

% -- tests for other outstanding issues
-- model facets of stream morphology to ascertain if consistent with encounter signatures
-- so far a lot of focus on gaps produced in encounters -- extra features we detected beside the GD-1 track suggest that further theoretical focus on scattered material is needed to fully understand its dynamical history
